FDT\thanks{Supported by organization x.}

### 2018-11-20 IPCO format/2ECFDT.tex
minor organization changes

In Section \ref{binaryfdt} our focus was on binary MIPs. In this section, in an attempt to extend FDT to 0,1,2 problems we introduce an FDT algorithm for a 2-edge-connected multigraph problem. Given a graph $G=(V,E)$ a multi-subset of edges $F$ of $G$ is a 2-edge-connected multigraph of $G$ if for each set $\emptyset\subset U \subset V$, the number of edge in $F$ that have one endpoint in $U$ and one not in $U$ is at least 2. In the 2EC problem, we are given non-negative costs on the edge of $G$ and the goal is to find the minimum cost 2-edge-connected multigraph of $G$. Notice that, no optimal solution ever takes 3 copies of an edge in 2EC, hence we assume that we can take an edge at most 2 times. The natural linear programming relaxation is $\EC(G) = \{x\in [0,2]^E: x(\delta(U))\geq 2 \mbox{ for } \emptyset \subset U \subset V\}$. Notice that $\dom(\EC(G))\cap [0,2]^{E} = \EC(G)$, since 2EC is a covering problem. We want to prove the following theorem.

\FDTEC*

We do not know the exact value for $g_{\EC}$, but we know $\frac{6}{5} \leq g_{\EC} \leq \frac{3}{2}$ \cite{carr-ravi,Wolsey1980}. Also, we need to remark that polyhedral version of Christofides' algorithm provides a $\frac{3}{2}$-approximation for 2EC, i.e. we already have an algorithm with $C\leq \frac{3}{2}$. However, we show later in Section \ref{experiment} that in practice the constant $C$ for the FDT algorithm for 2EC is much better than $\frac{3}{2}$.

The FDT algorithm for 2EC is very similar to the one for binary MIPs, but there are some differences as well. First, we need a branching lemma. Observe that  the following branching lemma is essentially a translation of Lemma \ref{LPClemma} for 0,1,2 problems expect for one additional clause.

>>>>

In Section \ref{binaryfdt} our focus was on binary MIPs. In this section, in an attempt to extend FDT to 0,1,2 problems we introduce an FDT algorithm for a 2-edge-connected multigraph problem. Given a graph $G=(V,E)$ a multi-subset of edges $F$ of $G$ is a 2-edge-connected multigraph of $G$ if for each set $\emptyset\subset U \subset V$, the number of edge in $F$ that have one endpoint in $U$ and one not in $U$ is at least 2. In the 2EC problem, we are given non-negative costs on the edge of $G$ and the goal is to find the minimum cost 2-edge-connected multigraph of $G$. Notice that, no optimal solution ever takes 3 copies of an edge in 2EC, hence we assume that we can take an edge at most 2 times. The natural linear programming relaxation is $\EC(G) = \{x\in [0,2]^E: x(\delta(U))\geq 2 \mbox{ for } \emptyset \subset U \subset V\}$. Notice that $\dom(\EC(G))\cap [0,2]^{E} = \EC(G)$, since 2EC is a covering problem. We want to prove Theorem \ref{FDT2EC}.
We do not know the exact value for $g_{\EC}$, but we know $\frac{6}{5} \leq g_{\EC} \leq \frac{3}{2}$ \cite{carr-ravi,Wolsey1980}. Also, we need to remark that polyhedral version of Christofides' algorithm provides a $\frac{3}{2}$-approximation for 2EC, i.e. we already have an algorithm with $C\leq \frac{3}{2}$. However, we showed in Section \ref{experiment} that in practice the constant $C$ for the FDT algorithm for 2EC is much better than $\frac{3}{2}$ for fundamental extreme points with 10 vertices.

The FDT algorithm for 2EC is very similar to the one for binary MILPs, but there are some differences as well. A natural thing to do is to have three branches for each node of the FDT tree, however, the branches that are equivalent to setting a variable to $1$, might need further decomposition. That is the main difficulty when dealing with $\{0,1,2\}$-MILPs.

First, we need a branching lemma. Observe that  the following branching lemma is essentially a translation of Lemma \ref{LPClemma} for 0,1,2 problems expect for one additional clause.

### 2018-11-20 IPCO format/FDT.tex
minor organization changes

\begin{document}
%
\title{FDT\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Robert Carr\inst{1}\orcidID{} \and
Arash Haddadan\inst{2}\orcidID{} \and
Cynthia Phillips\inst{3}\orcidID{}}
%
\authorrunning{R. Carr, A. Haddadan, C. Phillips}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{University of New Mexico, Albuquerque NM 87131, USA\\
\email{bobcarr@unm.}\\   \and
Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
\email{ahaddada@cmu.edu}\and
Sandia National Laboratories, Albuquerque, NM 87185, USA\\
\email{caphill@sandia.gov}}
%
\maketitle              % typeset the header of the con	tribution
%
\begin{abstract}
We present a new algorithm for finding a feasible solution for a mixed-integer linear program. The algorithm runs in polynomial time and is guaranteed to find a feasible integer solution provided the
integrality gap is bounded. The algorithm is based on convex decomposition of scaled linear-
programming relaxations, so in general it provides a suite of integer solutions. Because of the
relationship between convex decomposition and integrality gaps, this algorithm can be seen as an approximation algorithm. We apply our algorithm our algorithm to a class of 
fractional extreme points for two known problems in combinatorial optimization: the 2-edge-connected spanning subgraph problem and the tree augmentaion problem. These computational experiments show that our algorithm can be used as a tool to evaluate the integrality gap of integer programs with their linear relaxation. Finally we provide a stronger characterization of integrality gap for a class of covering problems than that of \cite{goemans}.

\keywords{Mixed-integer linear programming  \and  Integrality gap \and convex combinations.}
\end{abstract}
%
%
%
\input{introduction.tex}
\input{binaryFDT.tex}
\input{2ECFDT.tex}
\input{computational}
\iffalse{
\input{strongerCV}
}\fi

@@

\end{thebibliography}

\appendix
\section{Proof of Lemma 4}\label{lemma4}
	First, we need to show that in any iteration $\ell=  0,\ldots,t-1$ of Algorithm \ref{domtoIPalg} the $\DOMtoS(x^{\ell})$ is feasible. We show something stronger. For $\ell=0,\ldots,t-1$ let
	\begin{align*}
	\LP^{(\ell)}&= \{(z,w)\in P\; : \; z\leq x^{(\ell)} \mbox{ and } z_j=x_j^{(\ell)} \mbox{ for } j=1,\ldots,\ell\}, \text{ and}\\
	\IP^{(\ell)}&= \{(z,w)\in \LP^{(\ell)}\; : \; z\in \{0,1\}^n\}.
	\end{align*}
	Notice that if $\LP^{(\ell)}$ is a non-empty set then $\DOMtoS(x^{(\ell)})$ is feasible. We show by induction on $\ell$ that $\LP^{(\ell)}$ and $\IP^{(\ell)}$ are not empty sets for $\ell=0,\ldots,t-1$. First notice that $\LP^{(0)}$ is clearly feasible since by definition $(x^{(0)},y^{(0)})\in \dom(P)$, meaning there exists $(z,w)\in P$ such that $z\leq x^{(0)}$. By Theorem \ref{CV}, there exists $(\tilde{z}^i,\tilde{w}^i) \in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz$. Hence, $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz\leq gx^{(0)}$. So if $x^{(0)}_j=0$, then $ \sum_{i=1}^{k}\theta_i \tilde{z}_j^i =0$, which implies that $\tilde{z}^i_j=0$ for all $i=1,\ldots,k$ and $j= 1,\ldots,n$ where $x^{(0)}_j=0$. Hence, $z^i\leq x^{(0)}$ for $i=1,\ldots,k$. Therefore $(\tilde{z}^i,\tilde{w}^i)\in \IP^{(0)}$ for $i=1,\ldots,k$, which implies $\IP^{(0)}\neq \emptyset$.

	Now assume $\IP^{(\ell)}$ is non-empty for some $\ell \in \{0,\ldots,t-2\}$. Since $\IP^{(\ell)}\subseteq\LP^{(\ell)}$ we have $\LP^{(\ell)}\neq \emptyset$ and hence the $\DOMtoS(x^{(\ell)})$ has an optimal solution $(z^*,w^*)$.

	We consider two cases. In the first case, we have $z^*_{\ell+1}=0$. In this case we have $x^{(\ell+1)}_{\ell+1}=0$. Since $z^*\leq x^{(\ell+1)}$, we have $(z^*,w^*)\in \LP^{(\ell+1)}$. Also, $(z^*,w^*)\in P$. By Theorem \ref{CV} there exists $(\tilde{z}^i,\tilde{w}^i)\in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$ . We have
	\begin{equation}
	\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}
	\end{equation}
	So for $j\in \{1,\ldots,n\}$ where $x^{(\ell+1)}_j=0$, we have $z^i_j=0$ for $i=1,\ldots,k$. Hence, $\tilde{z}^i\leq x^{(\ell+1)}$ for $i=1,\ldots,k$. Hence, there exists $(z,w)\in S$ such that $z\leq x^{(\ell+1)}$. We claim that $(z,w)\in \IP^{(\ell+1)}$. If $(z,w)\notin \IP^{(\ell+1)}$ we must have $1\leq j \leq \ell$ such that $z_j < x^{(\ell+1)}_{j}$, and thus $z_j = 0$ and $x^{(\ell+1)}_j=1$. Without loss of generality assume $j$ is minimum number satisfying $z_j < x^{(\ell+1)}_{j}$. Consider iteration $j$ of Algorithm \ref{domtoIPalg}. Notice that $z\leq x^{(\ell+1)}\leq x^{(j)}$. We have $x^{(j)}_j=1$ which implies when we solved $\DOMtoS(x^{(j-1)})$ the optimal value was strictly larger than zero. However, $(z,w)$ is a feasible solution to $\DOMtoS(x^{(j-1)})$ and gives an objective value of 0. This is a contradiction, so $(z,w)\in \IP^{(\ell+1)}$.

	Now for the second case, assume $z^*_{\ell+1} > 0$. We have $x^{(\ell+1)}_{\ell+1}=1$. Notice that for each point $z\in \LP^{(\ell)}$ we have $z_{\ell+1} >0$, so for each $z\in \IP^{(\ell)}$ we have $z_{\ell+1}>0$, i.e. $z_{\ell+1}=1$. This means that $(z,w)\in \IP^{(\ell+1)}$, and $\IP^{(\ell+1)} \neq \emptyset$.

	Now consider $(x^{(t)},y^{(t)})$. Let $(z,y^{(t)})$ be the optimal solution to $\LP^{(t-1)}$. If $x^{(t)} = 0$, we have $x^{(t)} = z$, which implies that $(x^{(t)},y^{(t)})\in P$, and since $x^{(t)}\in \{0,1\}^n$ we have $(x^{(t)},y^{(t)})\in S$. If $x^{(t)} =1$, it must be the case that $z_t > 0$. By the argument above there is a point $(z',w')\in \IP^{(t-1)}$. We show that $x^{(t)} = z'$. Observe that for $j=1,\ldots,n-1$ we have $z'_j= x_j^{(t-1)}=x_j^{(t)}$. We just need to show that $z'_j = 1$. Assume $z'_j = 0$ for contradiction, then $(z',w')\in \LP^{(t-1)}$ has objective value of $0$ for $\DOMtoS(x^{(t-1)})$, this is a contradiction to $(z,w)$ being the optimal solution.
\end{document}

>>>>

\begin{document}
%
\title{FDT\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Robert Carr\inst{1}\orcidID{} \and
Arash Haddadan\inst{2}\orcidID{} \and
Cynthia Phillips\inst{3}\orcidID{}}
%
\authorrunning{R. Carr, A. Haddadan, C. Phillips}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{University of New Mexico, Albuquerque NM 87131, USA\\
\email{bobcarr@unm.}\\   \and
Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
\email{ahaddada@cmu.edu}\and
Sandia National Laboratories, Albuquerque, NM 87185, USA\\
\email{caphill@sandia.gov}}
%
\maketitle              % typeset the header of the con	tribution
%
\begin{abstract}
We present a new algorithm for finding a feasible solution for a mixed-integer linear program. The algorithm runs in polynomial time and is guaranteed to find a feasible integer solution provided the
integrality gap is bounded. The algorithm is based on convex decomposition of scaled linear-
programming relaxations, so in general it provides a suite of integer solutions. Because of the
relationship between convex decomposition and integrality gaps, this algorithm can be seen as an approximation algorithm. We apply our algorithm our algorithm to a class of 
fractional extreme points for two known problems in combinatorial optimization: the 2-edge-connected spanning subgraph problem and the tree augmentation problem. These computational experiments show that our algorithm can be used as a tool to evaluate the integrality gap of integer programs with their linear relaxation. Finally we provide a stronger characterization of integrality gap for a class of covering problems than that of \cite{goemans}.

\keywords{Mixed-integer linear programming  \and  Integrality gap \and convex combinations.}
\end{abstract}
%
%
%
\input{introduction.tex}
\input{binaryFDT.tex}
\input{computational}
\iffalse{
\input{strongerCV}
}\fi

@@

\end{thebibliography}
\newpage
\appendix

\input{2ECFDT.tex}

\end{document}

### 2018-11-20 IPCO format/binaryFDT.tex
minor organization changes

If the optimal value to $\DOMtoS(x^{(\ell)})$ is 0, then let $x^{(\ell+1)}_{\ell+1} = 0$. Otherwise if the optimal value is strictly positive let $x^{(\ell+1)}_{\ell+1} = 1$. Let $x^{(\ell+1)}_j = x^{(\ell)}_j$ for $j\in \{1,\ldots,n\}\setminus \{\ell+1\}$. This procedure is the DomToIP algorithm.
\iffalse{
\begin{algorithm}[H]
	\KwIn{$(x,y)\in \dom(S)$}
	\KwOut{$(x^{(t)},y^{(t)}) \in S$, $x^{(t)}\leq x$}
	$x^{(0)}\leftarrow x$\\
	\For{$\ell = 0$ \textbf{to} $t-1$}{
		$x^{(\ell+1)} \leftarrow x^{(\ell)}$\\
		$\eta \leftarrow$ optimal value of $ \DOMtoS(x^{(\ell)})$\\
		$y^{(\ell+1)}\leftarrow$ optimal solution for $w$ variables in $ \DOMtoS(x^{(\ell)})$\\
		\eIf{$\eta = 0$}{
			$x^{(\ell+1)}_{\ell+1} \leftarrow 0$\
		}{
			$x^{(\ell+1)}_{\ell+1} \leftarrow 1$
		}
	}
	\label{domtoIPalg}
	\caption{The DomToIP algorithm}
\end{algorithm}
}\fi
The following lemma proves Theorem \ref{domtoIP}.
\begin{lemma}
	Given $(x,y)\in \dom(P)$, DomToIP algorithm correctly finds $(x^{(t)},y^{(t)})\in S$ in polynomial time.
\end{lemma}
The proof is in Appendix \ref{lemma4}.

>>>>

If the optimal value to $\DOMtoS(x^{(\ell)})$ is 0, then let $x^{(\ell+1)}_{\ell+1} = 0$. Otherwise if the optimal value is strictly positive let $x^{(\ell+1)}_{\ell+1} = 1$. Let $x^{(\ell+1)}_j = x^{(\ell)}_j$ for $j\in \{1,\ldots,n\}\setminus \{\ell+1\}$. This procedure is the DomToIP algorithm.
\iffalse{
\begin{algorithm}[H]
	\KwIn{$(x,y)\in \dom(S)$}
	\KwOut{$(x^{(t)},y^{(t)}) \in S$, $x^{(t)}\leq x$}
	$x^{(0)}\leftarrow x$\\
	\For{$\ell = 0$ \textbf{to} $t-1$}{
		$x^{(\ell+1)} \leftarrow x^{(\ell)}$\\
		$\eta \leftarrow$ optimal value of $ \DOMtoS(x^{(\ell)})$\\
		$y^{(\ell+1)}\leftarrow$ optimal solution for $w$ variables in $ \DOMtoS(x^{(\ell)})$\\
		\eIf{$\eta = 0$}{
			$x^{(\ell+1)}_{\ell+1} \leftarrow 0$\
		}{
			$x^{(\ell+1)}_{\ell+1} \leftarrow 1$
		}
	}
	\label{domtoIPalg}
	\caption{The DomToIP algorithm}
\end{algorithm}
}\fi
The following lemma proves Theorem \ref{domtoIP}.
\begin{lemma}
	Given $(x,y)\in \dom(P)$, DomToIP algorithm correctly finds $(x^{(t)},y^{(t)})\in S$ in polynomial time.
\end{lemma}

\begin{proof}
	First, we need to show that in any iteration $\ell=  0,\ldots,t-1$ of Algorithm \ref{domtoIPalg} the $\DOMtoS(x^{\ell})$ is feasible. We show something stronger. For $\ell=0,\ldots,t-1$ let
	\begin{align*}
	\LP^{(\ell)}&= \{(z,w)\in P\; : \; z\leq x^{(\ell)} \mbox{ and } z_j=x_j^{(\ell)} \mbox{ for } j=1,\ldots,\ell\}, \text{ and}\\
	\IP^{(\ell)}&= \{(z,w)\in \LP^{(\ell)}\; : \; z\in \{0,1\}^n\}.
	\end{align*}
	Notice that if $\LP^{(\ell)}$ is a non-empty set then $\DOMtoS(x^{(\ell)})$ is feasible. We show by induction on $\ell$ that $\LP^{(\ell)}$ and $\IP^{(\ell)}$ are not empty sets for $\ell=0,\ldots,t-1$. First notice that $\LP^{(0)}$ is clearly feasible since by definition $(x^{(0)},y^{(0)})\in \dom(P)$, meaning there exists $(z,w)\in P$ such that $z\leq x^{(0)}$. By Theorem \ref{CV}, there exists $(\tilde{z}^i,\tilde{w}^i) \in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz$. Hence, $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz\leq gx^{(0)}$. So if $x^{(0)}_j=0$, then $ \sum_{i=1}^{k}\theta_i \tilde{z}_j^i =0$, which implies that $\tilde{z}^i_j=0$ for all $i=1,\ldots,k$ and $j= 1,\ldots,n$ where $x^{(0)}_j=0$. Hence, $z^i\leq x^{(0)}$ for $i=1,\ldots,k$. Therefore $(\tilde{z}^i,\tilde{w}^i)\in \IP^{(0)}$ for $i=1,\ldots,k$, which implies $\IP^{(0)}\neq \emptyset$.

	Now assume $\IP^{(\ell)}$ is non-empty for some $\ell \in \{0,\ldots,t-2\}$. Since $\IP^{(\ell)}\subseteq\LP^{(\ell)}$ we have $\LP^{(\ell)}\neq \emptyset$ and hence the $\DOMtoS(x^{(\ell)})$ has an optimal solution $(z^*,w^*)$.

	We consider two cases. In the first case, we have $z^*_{\ell+1}=0$. In this case we have $x^{(\ell+1)}_{\ell+1}=0$. Since $z^*\leq x^{(\ell+1)}$, we have $(z^*,w^*)\in \LP^{(\ell+1)}$. Also, $(z^*,w^*)\in P$. By Theorem \ref{CV} there exists $(\tilde{z}^i,\tilde{w}^i)\in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$ . We have
	\begin{equation}
	\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}
	\end{equation}
	So for $j\in \{1,\ldots,n\}$ where $x^{(\ell+1)}_j=0$, we have $z^i_j=0$ for $i=1,\ldots,k$. Hence, $\tilde{z}^i\leq x^{(\ell+1)}$ for $i=1,\ldots,k$. Hence, there exists $(z,w)\in S$ such that $z\leq x^{(\ell+1)}$. We claim that $(z,w)\in \IP^{(\ell+1)}$. If $(z,w)\notin \IP^{(\ell+1)}$ we must have $1\leq j \leq \ell$ such that $z_j < x^{(\ell+1)}_{j}$, and thus $z_j = 0$ and $x^{(\ell+1)}_j=1$. Without loss of generality assume $j$ is minimum number satisfying $z_j < x^{(\ell+1)}_{j}$. Consider iteration $j$ of Algorithm \ref{domtoIPalg}. Notice that $z\leq x^{(\ell+1)}\leq x^{(j)}$. We have $x^{(j)}_j=1$ which implies when we solved $\DOMtoS(x^{(j-1)})$ the optimal value was strictly larger than zero. However, $(z,w)$ is a feasible solution to $\DOMtoS(x^{(j-1)})$ and gives an objective value of 0. This is a contradiction, so $(z,w)\in \IP^{(\ell+1)}$.

	Now for the second case, assume $z^*_{\ell+1} > 0$. We have $x^{(\ell+1)}_{\ell+1}=1$. Notice that for each point $z\in \LP^{(\ell)}$ we have $z_{\ell+1} >0$, so for each $z\in \IP^{(\ell)}$ we have $z_{\ell+1}>0$, i.e. $z_{\ell+1}=1$. This means that $(z,w)\in \IP^{(\ell+1)}$, and $\IP^{(\ell+1)} \neq \emptyset$.

	Now consider $(x^{(t)},y^{(t)})$. Let $(z,y^{(t)})$ be the optimal solution to $\LP^{(t-1)}$. If $x^{(t)} = 0$, we have $x^{(t)} = z$, which implies that $(x^{(t)},y^{(t)})\in P$, and since $x^{(t)}\in \{0,1\}^n$ we have $(x^{(t)},y^{(t)})\in S$. If $x^{(t)} =1$, it must be the case that $z_t > 0$. By the argument above there is a point $(z',w')\in \IP^{(t-1)}$. We show that $x^{(t)} = z'$. Observe that for $j=1,\ldots,n-1$ we have $z'_j= x_j^{(t-1)}=x_j^{(t)}$. We just need to show that $z'_j = 1$. Assume $z'_j = 0$ for contradiction, then $(z',w')\in \LP^{(t-1)}$ has objective value of $0$ for $\DOMtoS(x^{(t-1)})$, this is a contradiction to $(z,w)$ being the optimal solution.\end{proof}

### 2018-11-20 IPCO format/computational.tex
minor organization changes

\section{Computational experiments with FDT}\label{experiment}
We implement FDT to two covering problem. First, the tree argumentation problem (TAP) where given a tree $T=(V,E)$, and a set of link $L$ between the vertices in $V$ and costs $c\in \bbbr^{L}_{\geq 0}$ we with to find minimum cost subset $L'$ of $L$ such that $T+L'$ is 2-edge-connected. For $\ell\in L$, let $P_\ell$ be the set of edges in the unique path between the endpoints of $\ell$ in $T$. For TAP, $S(\mbox{TAP})=\{x\in \bbbz^{L}_{\geq 0}: \sum_{\ell: e\in P_\ell}x_\ell \geq 1, \mbox{ for $e\in E$}\}$. Relaxing the integrality constraint we get $P(\mbox{TAP})$. It is been shown that $\frac{3}{2}\leq g({\mbox{TAP}})\leq 2$ \cite{fj,32gap}. We applied the binary FDT algorithm on a set of 264 fractional extreme points of $P(\mbox{TAP})$. The result are summarized in Table \ref{tableTAP}. 
\begin{table}[h]
	\centering
	  \begin{tabular}{c c c c c}
	  \toprule
	  	& $C\in [1.1,1.2]\;$ & $\;C\in (1.2,1.3]\;$ &
               $\;C\in (1.3,1.4]$ &\; $C\in (1.4,1.5]\;$ \\ \midrule
	  	TAP & $36$ & $66$ & $170$ & $10$\\  \bottomrule \\
	  \end{tabular}\caption{FDT impletemented applied to 264 randomly generated TAP instances with fractional extreme points: 138 of the 264 have $74$ variables, so the theoretical guarantee of Theorem \ref{binaryFDT} is at least $(1.5)^{74}$. For the rest, the number of variables in $250$.}
	  \label{tableTAP}
\end{table}
Next we implemented the FDT for 2EC on a 963 fractional extreme points of $\EC(G)$. These points are obtained by considering all fundamental vertices with $10$ and $12$ vertices (See \cite{CV} for the definition of fundamental vertices). The results are summarized in Table \ref{table2EC}. 
\begin{table}[h]
	\centering
	  \begin{tabular}{c c c c c}
	  	\toprule
	  	& $C\in [1.08,1.11]\;$ & $\;C\in (1.11,1.14]\;$ &
               $\;C\in (1.14,1.17]$ &\; $C\in (1.17,1.2]\;$ \\ \midrule
	  	2EC & $79$ & $201$ & $605$ & $78$ \\ \bottomrule\\
	  \end{tabular}\caption{FDT for $\EC$ implemented applied to all fundamental extreme points with 10 and 12 vertices. The number of variables for a fundamental extreme point with $k$ vertices is $\frac{3k}{2}$ and the lower bound on $g_\EC$ is $\frac{6}{5}$.}
	  \label{table2EC}
\end{table}
We also implemented polyhedral version of Christofides' algorithm \cite{Wolsey1980} and compared its performance on fundamental extreme points with 10 vertices. The result are in Figure \ref{fdtvschris}.
\begin{figure*}%
\centering
\includegraphics[width=8cm]{"fdt vs christofides".png}}
\caption{Christofides' algorithm vs FDT on all fundamental extreme points with 10 vertices.}
\label{fdtvschris}
\end{figure*}

>>>>

\section{Computational experiments with FDT}\label{experiment}
\begin{figure}[h!]
\centering
\includegraphics[width=5.5cm]{"fdt vs christofides".png}
\caption{Christofides' algorithm vs FDT on all fundamental extreme points with 10 vertices.}
\label{fdtvschris}
\end{figure}
We implement FDT to two covering problem. First, the tree argumentation problem (TAP) where given a tree $T=(V,E)$, and a set of link $L$ between the vertices in $V$ and costs $c\in \bbbr^{L}_{\geq 0}$ we with to find minimum cost subset $L'$ of $L$ such that $T+L'$ is 2-edge-connected. For $\ell\in L$, let $P_\ell$ be the set of edges in the unique path between the endpoints of $\ell$ in $T$. For TAP, $S(\mbox{TAP})=\{x\in \bbbz^{L}_{\geq 0}: \sum_{\ell: e\in P_\ell}x_\ell \geq 1, \mbox{ for $e\in E$}\}$. Relaxing the integrality constraint we get $P(\mbox{TAP})$. It is been shown that $\frac{3}{2}\leq g({\mbox{TAP}})\leq 2$ \cite{fj,32gap}. We applied the binary FDT algorithm on a set of 264 fractional extreme points of $P(\mbox{TAP})$. The result are summarized in Table \ref{tableTAP}. 
\begin{table}[h]
	\centering
	  \begin{tabular}{c c c c c}
	  \toprule
	  	& $C\in [1.1,1.2]\;$ & $\;C\in (1.2,1.3]\;$ &
               $\;C\in (1.3,1.4]$ &\; $C\in (1.4,1.5]\;$ \\ \midrule
	  	TAP & $36$ & $66$ & $170$ & $10$\\  \bottomrule \\
	  \end{tabular}\caption{FDT implemented applied to 264 randomly generated TAP instances with fractional extreme points: 138 of the 264 have $74$ variables, so the theoretical guarantee of Theorem \ref{binaryFDT} is at least $(1.5)^{74}$. For the rest, the number of variables in $250$.}
	  \label{tableTAP}
\end{table}
\vspace*{-30pt}
Next we implemented the FDT for 2EC on a 963 fractional extreme points of $\EC(G)$. These points are obtained by considering all fundamental vertices with $10$ and $12$ vertices (See \cite{CV} for the definition of fundamental vertices). The results are summarized in Table \ref{table2EC}. 
\begin{table}[h]
	\centering
	  \begin{tabular}{c c c c c}
	  	\toprule
	  	& $C\in [1.08,1.11]\;$ & $\;C\in (1.11,1.14]\;$ &
               $\;C\in (1.14,1.17]$ &\; $C\in (1.17,1.2]\;$ \\ \midrule
	  	2EC & $79$ & $201$ & $605$ & $78$ \\ \bottomrule\\
	  \end{tabular}	\caption{FDT for $\EC$ implemented applied to all fundamental extreme points with 10 and 12 vertices. The number of variables for a fundamental extreme point with $k$ vertices is $\frac{3k}{2}$ and the lower bound on $g(\EC)$ is $\frac{6}{5}$}.
	  \label{table2EC}
\end{table}
\vspace*{-30pt}
We also implemented polyhedral version of Christofides' algorithm \cite{Wolsey1980} and compared its performance on fundamental extreme points with 10 vertices. The result are in Figure \ref{fdtvschris}.

### 2018-11-20 IPCO format/introduction.tex
minor organization changes

The \textit{Fractional Decomposition Tree} algorithm (henceforth FDT) is a polynomial time algorithm that given a point $x\in P(I)$ produces a convex combination of feasible point in $S(I)$ that are dominates by a ``factor" of $x$. If this factor is $g_I$, it would settle Question \ref{question2}, however we can only guarantee a factor of $g_I^|\spp(x)|$. FDT relies on iteratively solving linear programs that are about the same size as the description of $P(I)$.

@@

\begin{restatable}{theorem}{FDTEC}
	\label{FDT2EC}
	Let $G=(V,E)$ and $x$ be an extreme point of  $\EC(G)$. The FDT algorithm for 2EC produces $\lambda\in [0,1]^k$ and 2-edge-connected multigraphs $F_1,\ldots,F_k$ such that $k\leq O(|V|)$, $\sum_{i=1}^{k}\lambda_i \chi^{F_i}\leq Cx^*$, and $\sum_{i=1}^{k}\lambda_i = 1$. Moreover, $C\leq g_{\EC}^{O(|V|)}$, where $g_{\EC}$ is the integrality gap of the 2-edge-connected multigraph problem with respect to formulation in (\ref{2ECpol}) 
\end{restatable}

>>>>

The \textit{Fractional Decomposition Tree} algorithm (henceforth FDT) is a polynomial time algorithm that given a point $x\in P(I)$ produces a convex combination of feasible point in $S(I)$ that are dominates by a ``factor" of $x$. If this factor is $g_I$, it would settle Question \ref{question2}, however we can only guarantee a factor of $g_I^{|\spp(x)|}$. FDT relies on iteratively solving linear programs that are about the same size as the description of $P(I)$.

@@

\begin{restatable}{theorem}{FDTEC}
	\label{FDT2EC}
	Let $G=(V,E)$ and $x$ be an extreme point of  $\EC(G)$. The FDT algorithm for 2EC produces $\lambda\in [0,1]^k$ and 2-edge-connected multigraphs $F_1,\ldots,F_k$ such that $k\leq 2|V|-1$, $\sum_{i=1}^{k}\lambda_i \chi^{F_i}\leq Cx^*$, and $\sum_{i=1}^{k}\lambda_i = 1$. Moreover, $C\leq g({\EC})^{k}$, where $g({\EC})$ is the integrality gap of the 2-edge-connected multigraph problem with respect to formulation in (\ref{2ECpol}) 
\end{restatable}
